Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-04-23 WholePlotTrajectories.Rmd
html pages

Except for leaf cholorphyll content, which continued to increase for some T3 and T2 plots 30 years after disturbance, all traits and seed mass proportions displayed a unimodal trajectories.
The weighted means of communities specific maximum height at adult stage (*Hmax*), leaf toughness (*L_toughness*) and wood specific gravity (*WD*) remained significantly lower than their initial value and than these of the control plots (Figure \@ref(fig:CWM)).
The weighted means of bark thickness (*Bark_thick*) similarly remained substantilly higher than initially for all disturbed plots while the specfic leaf area (*SLA*) had almost recovered its initial value and this of the undisturbed plots at the end of the experiment.
Once again the maximum difference to initial state was correlated to the disturbance intensity ($\rho_{spearman}^{L_thickness}=0.67$,$\rho_{spearman}^{L_chloro}=0.45$,$\rho_{spearman}^{L_toughness}=-0.43$,$\rho_{spearman}^{SLA}=0.93$,$\rho_{spearman}^{WD}=-0.78$,$\rho_{spearman}^{Bark-thickness}=0.88$,$\rho_{spearman}^{Hmax}=-0.48$).

@@

The functional diversity followed a hump-back trajectory which maximum was positively correlated to the disturbance intensity ($\rho_{spearman}=$) and after 30 years, all disturbed plots had recovered diversities close to their initial values. 
Similar hump-back trajectories were followed by all leaf and stem functional traits and life history traits, to the exception of leaf chlorophyll content.
Although the return to initial values was still ongoing the recovery of functional diversity and average communities trait values was undeniable.
This translated the recovery of ecosystems processes [@Guariguata2001], as functional traits are the most direct link between biodiversity and ecosystem functioning [@Diaz2005].
Same recovery trajectories were followed by taxonomic and functional composition which argued for communities convergence and the maintenance of plots initial difference [@Hubbell1999;@Molino2001;@Baraloto2012a].
These compositon difference, and probably also some abiotic parameters, besides strongly determined the maximum and time path of the trajectories which, despite an homogeneous trend  were quite variable among plots.

>>>>

Except for leaf cholorphyll content, which continued to increase for some T3 and T2 plots 30 years after disturbance, all traits and seed mass proportions displayed a unimodal trajectories.
The weighted means of communities specific maximum height at adult stage (*Hmax*), leaf toughness (*L_toughness*) and wood specific gravity (*WD*) remained significantly lower than their initial value and than these of the control plots (Figure \@ref(fig:CWM)).
The weighted means of bark thickness (*Bark_thick*) similarly remained substantilly higher than initially for all disturbed plots while the specfic leaf area (*SLA*) had almost recovered its initial value and this of the undisturbed plots at the end of the experiment.
Once again the maximum difference to initial state was correlated to the disturbance intensity ($\rho_{spearman}^{L_thickness}=0.67$, $\rho_{spearman}^{L_chloro}=0.45$, $\rho_{spearman}^{L_toughness}=-0.43$, $\rho_{spearman}^{SLA}=0.93$, $\rho_{spearman}^{WD}=-0.78$, $\rho_{spearman}^{Bark-thickness}=0.88$, $\rho_{spearman}^{Hmax}=-0.48$).

@@

The functional diversity followed a hump-back trajectory which maximum was positively correlated to the disturbance intensity and after 30 years, all disturbed plots had recovered diversities close to their initial values. 
Similar hump-back trajectories were followed by all leaf and stem functional traits and life history traits, to the exception of leaf chlorophyll content.
Although the return to initial values was still ongoing the recovery of functional diversity and average communities trait values was undeniable.
This translated the recovery of ecosystems processes [@Guariguata2001], as functional traits are the most direct link between biodiversity and ecosystem functioning [@Diaz2005].
Same recovery trajectories were followed by taxonomic and functional composition which argued for communities convergence and the maintenance of plots initial difference [@Hubbell1999;@Molino2001;@Baraloto2012a].
These compositon difference, and probably also some abiotic parameters, besides strongly determined the maximum and time path of the trajectories which, despite an homogeneous trend  were quite variable among plots.
